---
title: "LogAir: Open pollution mapper"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: https://github.com/walkerke/neighborhood_diversity

---

```{r setup, include=FALSE}

library(shiny)
library(leaflet) # devtools::install_github('rstudio/leaflet')
library(highcharter) # devtools::install_github('jbkunst/highcharter')
library(plotly) # devtools::install_github('ropensci/plotly')
library(ggplot2) # devtools::install_github('hadley/ggplot2')
library(sp)
library(dplyr)
library(flexdashboard) # devtools::install_github('rstudio/flexdashboard')
library(rgeos)
library(mapproj)
library(maptools)
library(readr)
library(ggthemes)
library(DT)
library(anytime)

# Build dataframe
library("jsonlite")
url <- "https://api.logair.unige.ch/v1/service/device?device_id=LAJA-001"
df <- jsonlite::fromJSON(url)
df <- df %>%
  mutate(datetime = anytime(timestamp_nix/1000)) %>%
  mutate(date = anydate(timestamp_nix/1000)) %>% 
  mutate(time = format(datetime, format = "%H:%M:%S"))

# Build base plot
base_graph <- ggplot(df, 
                     aes(transaction_id)) 

# Build base map

pal <- colorFactor(
  palette = c('green', 'yellow', 'orange', 'red', 'purple'),
  domain = df$pm_10
)

map <-  leaflet(df) %>% 
    addProviderTiles(providers$CartoDB.Positron) %>% 
    addCircles(
      popup = ~paste0(
        "<b>Device ID:</b> ", device_id,
        "<br><b>Date</b>: ", date,
        "<br><b>Time</b>: ", time,
        "<br><b>Temperature (C)</b> ", temperature,
        "<br><b>RH (%):</b> ", relative_humidity,
        "<br><b>PM10: </b> ", pm_10,
        "<br><b>PM2.5: </b> ", pm_2_5
        ),
      radius = 1,
      color = ~pal(pm_10),
      data = df
    )
  

```

Sidebar {.sidebar}
======================================================================

### Choose your parameters
<br>

```{r}
# Define inputs

textInput(inputId = "device", label = "Your device ID")

actionButton("goButton", "Get data")

dateRangeInput(inputId = "dates", 
               label = "Date range")


sliderInput(inputId = "hours", 
              label = "Hour range",
              dragRange = TRUE,
              value = c(7,9), min = 0, max = 24)

checkboxGroupInput('params', 
                   label = 'Select the parameter to plot', 
                   c( "PM2.5" = "pm25",
                       "PM10" = "pm10")
                   )

```

***
Some dummy text in the sidebar

Data by LogAir, all CC-BY 4.0

Overview
======================================================================

Row 
-----------------------------------------------------------------------

### Map

```{r}

renderLeaflet({
  map
  })

  
```

### PM concentration for a selected area (click on map)
```{r}
"Some chart"
```

Row
-----------------------------------------------------------------------

### All particulate matter values for this device

```{r}


renderPlot({ base_graph +
  geom_col(aes(y = pm_10, colour = "PM 10")) +
  geom_col(aes(y = pm_2_5, colour = "PM 2.5")) 
  })

# if pm25 true, base_graph+pm25, if if pm10 true, base_graph+pm10, else base_graph


```

Calendar
============================================================================

```{r}
# Recreate calendar heatmap
library(lubridate) # For date and time manipulation

dfsarasa  <-  tibble(
  dateCol = seq(
    dmy("01/01/2019"),
    dmy("31/12/2019"),
    "days"
  ),
  ValueCol = runif(365)
)

dfPlot <- dfsarasa %>% 
  mutate(weekday = wday(dateCol, label = T, week_start = 1), # can put week_start = 1 to start week on Monday
         month = month(dateCol, label = T),
         date = yday(dateCol),
         week = epiweek(dateCol))

# isoweek makes the last week of the year as week 1, so need to change that to week 53 for the plot
dfPlot$week[dfPlot$month=="Dec" & dfPlot$week ==1] = 53 

dfPlot <- dfPlot %>% 
  group_by(month) %>% 
  mutate(monthweek = 1 + week - min(week))

# Plot
# 
# dfPlot %>%
#   ggplot(aes(weekday,-week, fill = ValueCol)) +
#   geom_tile(colour = "white")  + 
#   geom_text(aes(label = day(dateCol)), size = 2.5, color = "black") +
#   theme(aspect.ratio = 1/8,
#         legend.position = "top",
#         legend.key.width = unit(3, "cm"),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         axis.text.y = element_blank(),
#         panel.grid = element_blank(),
#         axis.ticks = element_blank(),
#         panel.background = element_blank(),
#         legend.title.align = 0.5,
#         strip.background = element_blank(),
#         strip.text = element_text(face = "bold", size = 15),
#         panel.border = element_rect(colour = "grey", fill=NA, size=1),
#         plot.title = element_text(hjust = 0.5, size = 21, face = "bold",
#                                   margin = margin(0,0,0.5,0, unit = "cm"))) +
#   scale_fill_gradientn(colours = c("#6b9235", "white", "red"),
#                        values = scales::rescale(c(-1, -0.05, 0, 0.05, 1)), 
#                        name = "Values",
#                        guide = guide_colorbar(title.position = "top", 
#                                               direction = "horizontal")) +
#   facet_wrap(~month, nrow = 4, ncol = 3, scales = "free") +
#   labs(title = "Calendar heatmap 2019")


dfPlot %>%
  ggplot(aes(weekday,-week, fill = ValueCol)) +
  geom_tile(colour = "white")  + 
  geom_text(aes(label = day(dateCol)), size = 3) +
  theme(aspect.ratio = 1/2,
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        panel.background = element_blank(),
        strip.background = element_blank(),
        strip.text = element_text(face = "bold", size = 15),
        panel.border = element_rect(colour = "black", fill=NA, size=1)) +
  scale_fill_gradient2(midpoint = 0.5) +
  facet_wrap(~month, nrow = 4, ncol = 3, scales = "free") +
  labs(title = "Calendar heatmap 2019")

```

Raw data
============================================================================
```{r}
datatable(df[c("transaction_id", "date", "time", "device_id", "latitude", "longitude", "altitude", "temperature", "relative_humidity", "pm_2_5", "pm_10")],
          filter = 'top',
          rownames = FALSE)
```

About
============================================================================

Other about dummy text


<style>

#sidebar.section.sidebar {

  background-color: white; 
  font-family: "Open Sans", "Helvetica Neue", Helvetica, Arial, sans-serif !important;

}

.js-irs-0 .irs-bar {
border-top-color: #d01010;
border-bottom-color: #d01010;
} 

.js-irs-0 .irs-bar-edge {
border-color: #d01010;
}

.js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge, .js-irs-0 .irs-bar {
background: #a00;
}

</style>
